An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
last reference

\vskip 0.3in
]
\begin{abstract}
The aim of this paper is to present a complete system for off-line handwriting recognition.
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters.
Then we describe how to recognise characters with a deep neural network approach. 
Finally we present postprocessing techniques to correct mispredicted text. 
Our approach does not outperform state-of-the-art systems but hopes to provide a thorough elaboration for every step in handwriting recognition. 
\end{abstract}

@@

To be able to recognise the characters in a given text, we will first need to extract the words from the text before we can start evaluating the characters. This word extraction has many possible approaches, but in this paper we will focus solely on the word contouring approach.
This method uses a heuristic algorithm to extract the contours of the words from a given text, and through postprocessing we can rearrange these extracted words into lines.
The algorithm proposed is only to processes text images, and does not take into account images and other non-textual areas found in the text.
Dependant on the situation, additional techniques for page segmentation can be utilized. % , such as the Run-Length Smearing Algorithm, can be utilized.
% TODO:: Run length Smearing Algorithm reference --> ....

@@

The next step in the process is to extract the character images from the given word images.
Again, there is the choise between several different approaches.
In this paper we focus solely on a word oversegmentation approach to character extraction.
The purpose is to segment the words into the individual characters.
This will be done through initial oversegmentation of the word image, followed by postprocessing steps to remove the excess separation points to recover the original character images.

@@

\subsection{Oversegmentation correction}
In this section we provide techniques to verify the correctness of these segmentation points. 
\cite{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures. [6:39]
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.

@@

\subsubsection{Neural network}
The neural network we use to judge the potential segmentation points, is based on \cite{evalsplitpointsnn}. The paper explains how to use neural networks to classify the correctness of segmentation points. The discussed algorithm is as follows. Manual classification of segmentation points creates training data with two classes, correct and incorrect segmentation points.
For every of these segmentation points a pixel matrix is extracted surrounding the segmentation point. This pixel matrix is normalised in size.
Next, small windows of equal size are extracted from the pixel matrix and for each window the density is calculated. This is the number of black pixels divided by the total amount of pixels in the window.
With every matrix a corresponding label is encoded for storage in the training file, this label is encoded as 0.9 if the segmentation point is correct and 0.1 otherwise. Now these matrices and corresponding labels are used to train the neural network.

We take a slightly different approach and consider a deep neural network to tackle this problem. This allows us to use the power of convolutational layers to extract features, instead of manually creating features (features which show the density in this case).
We use one convolutional layer and three fully connected layers in our neural network. This neural network takes the actual image of the segmentation point as input (a pixel matrix of the pixels surrounding the splitting point) and returns a one-hot encoded vector indicating if the splitting is correct or incorrect. In order to create training data we created a small program to iterate over splitting points of handwritten words from the IAM dataset. \cite{iam}

This method allowed us to achieve an accuracy of 72 \%, which is still fairly low because of the difficulty of the problem and the small amount of traing data. However this is better than our accuracy with an implementation of the method described by \cite{evalsplitpointsnn}.
Segmentation points can now be filtered if the neural network decides a segmentation point is incorrect.

@@

Finally, other approaches can also be considered.
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks.
This concept is explained and applied by \cite{presham}.
\section*{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}

>>>>

\vskip 0.3in
]
% Notes:
%  redo the preprocessing experiment and explain why some techniques increase the accuracy more than others.
\begin{abstract}
The aim of this paper is to present a complete system for off-line handwriting recognition.
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters.
Then we describe how to recognise characters with a deep neural network approach.
Finally we presentf postprocessing techniques to correct mispredicted text.
\end{abstract}

@@

To be able to recognise the characters in a given text, we will first need to extract the words from the text before we can start evaluating the characters. This word extraction has many possible approaches, but in this paper we will focus solely on the word contouring approach, as pointed out by following paper \cite{WordSegm} as being a good word extraction approach.
This method uses a heuristic algorithm to extract the contours of the words from a given text, and through postprocessing we can rearrange these extracted words into lines.
The algorithm proposed is only to processes text images, and does not take into account images and other non-textual areas found in the text.
Dependant on the situation, additional techniques for page segmentation can be utilized. % , such as the Run-Length Smearing Algorithm, can be utilized.
% TODO:: Run length Smearing Algorithm reference --> ....

@@

The next step in the process is to extract the character images from the given word images.
Again, there is the choise between several different approaches.
In this paper we focus solely on a word oversegmentation approach to character extraction, as can be found described here \cite{CharSegm} and \cite{CharSegmOld}.
The purpose is to segment the words into the individual characters.
This will be done through initial oversegmentation of the word image, followed by postprocessing steps to remove the excess separation points to recover the original character images.

@@

\subsection{Oversegmentation correction}
In this section we provide techniques to verify the correctness of these segmentation points. 
\citep{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures.
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.

@@

\subsubsection{Neural network}
The neural network we use to judge the potential segmentation points, is based on \citep{evalsplitpointsnn}. The paper explains how to use neural networks to classify the correctness of segmentation points. The discussed algorithm is as follows. Manual classification of segmentation points creates training data with two classes, correct and incorrect segmentation points.
For every of these segmentation points a pixel matrix is extracted surrounding the segmentation point. This pixel matrix is normalised in size.
Next, small windows of equal size are extracted from the pixel matrix and for each window the density is calculated. This is the number of black pixels divided by the total amount of pixels in the window.
With every matrix a corresponding label is encoded for storage in the training file, this label is encoded as 0.9 if the segmentation point is correct and 0.1 otherwise. Now these matrices and corresponding labels are used to train the neural network.

We take a slightly different approach and consider a deep neural network to tackle this problem. This allows us to use the power of convolutational layers to extract features, instead of manually creating features (features which show the density in this case).
We use one convolutional layer and three fully connected layers in our neural network. This neural network takes the actual image of the segmentation point as input (a pixel matrix of the pixels surrounding the splitting point) and returns a one-hot encoded vector indicating if the splitting is correct or incorrect. In order to create training data we created a small program to iterate over splitting points of handwritten words from the IAM dataset. \citep{iam}

This method allowed us to achieve an accuracy of 72 \%, which is still fairly low because of the difficulty of the problem and the small amount of traing data. However this is better than our accuracy with an implementation of the method described by \citep{evalsplitpointsnn}.
Segmentation points can now be filtered if the neural network decides a segmentation point is incorrect.

@@

Finally, other approaches can also be considered.
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks.
This concept is explained and applied by \citep{presham}.
%%% Dit is jouw oude tekst %%%
There are a lot of steps in this paper from which we can draw conclusions.
The segregation of a text image in word images is
Word extraction is a problem

Character segmentation is another ..
The proposed oversegmentation serves the intended purpose, however more rule-based postprocessing steps are needed to reduce the amount of incorrect segmentation points the neural network has to process.
Combinations with other approaches are also more likely provide better results.

The neural network ..

The neural network
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}
